Hierarchical Controller Architecture for SDN

### 2013-11-05 presentation/ppt.tex
Ppt update

\frame{
\frametitle{Hierarchical Architecture}
\begin{itemize}
	\item Hierarchical Architecture
	\begin{itemize}
		\item Controllers' view do not span the whole network, but only the 'underlying network'
		\item Each controller behaves as a giant openflow switch for parent controller (Network Aggregation)
		\item Controller translates OFP commands and network updates between parent controller and underlying networks
	\end{itemize}
\end{itemize}
}

>>>>

\frame{
\frametitle{Hierarchical Architecture}
\begin{itemize}
	\item Controllers' view do not span the whole network, but only the 'underlying network'
	\item A controller behaves as an openflow switch for parent controller (Network Aggregation) and as a controller for its underlying network
	\item Controller translates OFP commands and network updates between parent controller and underlying networks
	\item Control applications run on each controller to set the network parameters in its underlying network
\end{itemize}
}

\frame{
\frametitle{Simulation}
\begin{itemize}
	\item Wrote a simulator to simulate a hierarchical controller architecture\footnote{code @ https://github.com/MugiwaraLuffy/ACN/tree/master/simulator/src/graph}
	\item A minimal API for control plane, data plane, controller behavior, etc have been defined
	\item A $Node$ is an element in the network which implements a control plane interface 
	\item A $Switch$ extends a $Node$ and contains a data plane
	\item A $Controller$ extends a $Node$ and implements standard controller API
	\item $DataNetwork$ contains all the switches which handle actual data packets
	\item $ControlNetwork$ contains hierarchical layers of controllers
\end{itemize}
}
